---
title: "Act3"
author: "BHH"
date: "February 12, 2020"
output: html_document
---

---
title: "Act_3"
author: "BHH"
date: "2/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
install.packages('devtools')
devtools::install_github("bomeara/phybase")
```

```{r}
library(rotl)
library(ape)
phy <- get_study_tree("ot_485", "tree1")
plot(phy, cex=0.3)
```

this is a lot of taxa...124 tips. We can narrow this. however, im slightly confused as to why Ntip(phy) drops all but ten. This is the same as phy3.. the -10 seems somewhat counter intuitive. Why isnt it 114 tips after dropping?
```{r}
library(geiger)
phy2 <- drop.random(phy, Ntip(phy) - 10)
phy3<- drop.random(phy, 114)
plot(phy2)
plot(phy3)
axisPhylo()
```
simulating genes to match the tree
```{r}
library(phybase)
gene.tree <- phybase::sim.coaltree.phylo(phy2, pop.size=1e-12)
plot(gene.tree)
```
We can plot the two trees together. This is cool
```{r}
library(phytools)
plot(cophylo(phy2, gene.tree, cbind(sort(phy2$tip.label), sort(gene.tree$tip.label))))
```

Even though the species seem to line up and gene tree matches species tree, lack of coalescence can occur, thus causing incongruence
```{r}
species.tree <- rcoal(7)
species.tree$edge.length <- species.tree$edge.length / (10*max(branching.times(species.tree)))
gene.tree <- phybase::sim.coaltree.phylo(species.tree)
plot(cophylo(species.tree, gene.tree, cbind(sort(species.tree$tip.label), sort(gene.tree$tip.label))))

```
lengthening tips to see if they agree
```{r}
tip.rows <- which(species.tree$edge[,2]<=Ntip(species.tree))
species.tree2 <- species.tree
species.tree2$edge.length[tip.rows] <- 100 + species.tree2$edge.length[tip.rows]
gene.tree2 <- phybase::sim.coaltree.phylo(species.tree2)
plot(cophylo(species.tree2, gene.tree2, cbind(sort(species.tree2$tip.label), sort(gene.tree2$tip.label))))
```
Manually changing branch lengths without resimulating
```{r}
species.tree2.clado <- compute.brlen(species.tree2)
gene.tree2.clado <- compute.brlen(gene.tree2)
plot(cophylo(species.tree2.clado, gene.tree2.clado, cbind(sort(species.tree2.clado$tip.label),
sort(gene.tree2.clado$tip.label))))


```